\documentclass[a4paper,11pt]{book}
\title{Test}
\author{Julio Casallo Tamayo}

\pagestyle{headings}

\usepackage{verbatim}
\usepackage{textcomp}
\usepackage[official]{eurosym}

% Contents table refs
\usepackage{hyperref}
\hypersetup{
    colorlinks,
    citecolor=black,
    filecolor=black,
    linkcolor=black,
    urlcolor=black
}

% Line under header
\usepackage{fancyhdr}% http://ctan.org/pkg/fancyhdr
\pagestyle{fancy}% Change page style to fancy


\begin{document}
  % Generates the title
  \maketitle

  % Generates the table of contents
  \tableofcontents

  \chapter{Things You Need To Know}

  \section{Testing}
  This is a document.

  It does not matter whether you enter one or   several    
  spaces after a word.
  An empty line starts a new paragraph.

  New \TeX users may miss whitespaces after a command.
  % renders wrong 
  Experienced \TeX{} users are \TeX perts, and know how to
  use whitespaces. % renders correct

  You can \textsl{lean} on me!

  Please, start a new line right here! \newline 
  Thank You!

  This an % stupid
  % Better: instructive <-----
  example: Supercal%
              ifragilist%
        icexpialidocious

  This is another \begin{comment}
    rather stupid, 
    but helpful
  \end{comment}
  example for embedding comments in your document.

  \include{tex/module1.tex}

  \chapter{Typesetting Text}


  \newpage

  \section{Testing new page}
  This is a new page

  `` Please press the `x' key ''

  daughter-in-law, X-rated\\
  pages 13--67\\
  yes---or no?\\
  $0$, $1$ and $-1$

  http://www.rich.edu/\~{}bush \\
  http://www.clever.edu/$\sim$demo

  read\slash write

  It's $-30\,^{\circ}\mathrm{C}$.
  I will soon start to 
  super-conduct.

  30 \textcelsius{} is
  85 \textdegree{}F.

  \texteuro
  \euro

  Not like this ... but like this:\\
  New York, Tokyo, Budapest, \ldots

  \Large Not shelfful\\
  but shelf\mbox{}ful

  \normalsize 
  H\^otel, na\"\i ve, \'el\`eve,\\
  sm\o rrebr\o d, !`Se\~norita!,\\
  Sch\"onbrunner Schlo\ss{} 
  Stra\ss e

  Mr.~Smith was happy to see her\\
  cf.~Fig.~5\\
  I like Basic\@. What about you?

  \section{Titles, Chapters and Sections}

  \subsection{This is a subsection}

  \paragraph{This is a paragraph}

\end{document}
